\thesistitle

### 2019-08-25 sections/background.tex
Small thesis chnages
Background

\section{Code clone terminology}\label{sec:terminology}
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and Jiang et al. \cite{jiang2007deckard}. A summary of these concepts can be found in Table~\ref{tab:clone-terminology}. The terms displayed in this table show how tokens in code map to clones.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} Begin line/column and end\\line/column of this node.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

@@

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
// File1.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// File2.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
// File3.java
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\end{parcolumns}
\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
\label{fig:cloneclasses}
\end{figure}

This example can be represented as a tree structure, as shown in Figure~\ref{fig:terminologyexample}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/TerminologyExample}
  \caption{Representation of Figure~\ref{fig:cloneclasses} using the terminology introduced in Table~\ref{tab:clone-terminology}}
  \label{fig:terminologyexample}
\end{figure}

@@

\section{Refactoring techniques}
In Martin Fowler's popular ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''}. He describes several techniques to deal with duplication, dependent on the context of the clone. In this section we describe the methods that we use in this study.

@@

\subsubsection{Pull up method}
A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \cite{fowler2018refactoring}. This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common. This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method). Anexample of this refactoring method is shown in Figure~\ref{fig:pullupmethod}.

@@

\subsubsection{Providing default implementations for common functionality}
In Java, C\#, Python and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number. Such interfaces can (in Java, C\# and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}. This gives an opportunity to make the relation between classes explicit and reduce duplication. It can be used in instances where creating a new parent class for duplicated classes is undesirable. An example of this is shown in Figure~\ref{fig:createinterfaceabstraction}, in which two unrelated types (Human and Radio) share a common property (making sound).

@@

%\subsection{Clone refactoring in relationship to its context}
% TODO: Sander - Deze subsectie lijkt hier niet helemaal op zn plek
%How to refactor clones is highly dependent on their context. Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class. If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure. If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves. So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class. This is highly relevant to the way in which the clone has to be refactored.

@@

\subsection{Maven}
For this study we perform a shallow analysis on external dependencies, in order to derive more context for internally used concepts. As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies. To limit the scope of this process, we decided to focus on only the \textit{Maven}\footnote{Apache Maven is a build automation system mainly used for Java: \url{https://maven.apache.org/}} build automation system.

>>>>

\section{Code clone terminology}\label{sec:terminology}
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use} and Jiang et al. \cite{jiang2007deckard}. A summary of these concepts can be found in Table~\ref{tab:clone-terminology}. The terms displayed in this table show how tokens in code map to clones. When detecting clones of a software system, we end up with a clone class collection. Each clone class denotes a set of duplicate fragments. We call these duplicate fragments clone instances. Each clone instance spans a number of statements/declarations. We refer to these statements and declarations as ``nodes''. Each node consists of a set of tokens.

\begin{table}[H]
\centering
%\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} \\ \midrule
\rowcolor[HTML]{EFEFEF}
T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular}  \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
C & Clone class \cite{bruntink2005use}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations. Each of these\\code fragments is called a\\``clone instance''.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
%R & Range & A part of a source code file. &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
 \bottomrule
\end{tabular}%
%}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

@@

This example can be represented as a tree structure, as shown in Figure~\ref{fig:terminologyexample}. This example uses the terminology introduced in Table~\ref{tab:clone-terminology}, together with some properties of clone instances and nodes. Each clone instance has a \textbf{range}, which denotes the line and column at which a code fragment starts and ends. Each clone instance is found in a certain \textbf{file}.

\begin{figure}[H]
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
// File1.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// File2.java
|\highlightDarkyellow|doA();
|\highlightDarkyellow|doB();
|\highlightYellow|doC();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
// File3.java
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\end{parcolumns}
\caption{Example of two clone classes.}
\label{fig:cloneclasses}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/TerminologyExample}
  \caption{Tree representation of Figure~\ref{fig:cloneclasses} using the terminology of Table~\ref{tab:clone-terminology}}
  \label{fig:terminologyexample}
\end{figure}

@@

\section{Refactoring techniques}
In Martin Fowler's popular ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''}. He describes several techniques to deal with duplication, dependent on the context of the clone. In this section we describe the techniques that we use in this study.

@@

\subsubsection{Pull up method}
A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \cite{fowler2018refactoring}. This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common. This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method). An example of this refactoring technique is shown in Figure~\ref{fig:pullupmethod}.

@@

\subsubsection{Providing default implementations for common functionality}
In Java, C\#, Python, and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number. Such interfaces can (in Java, C\# and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}. This gives an opportunity to make the relation between classes explicit and reduce duplication. It can be used in instances where creating a new parent class for duplicated classes is undesirable. An example of this is shown in Figure~\ref{fig:createinterfaceabstraction}, in which two unrelated types (Human and Radio) share a common property (making sound).

@@

%\subsection{Clone refactoring in relationship to its context}
%How to refactor clones is highly dependent on their context. Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class. If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure. If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves. So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class. This is highly relevant to the way in which the clone has to be refactored.

@@

\subsection{Maven}
For this study we perform an analysis on external dependencies, to derive more context for internally used concepts. As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies. To limit the scope of this process, we decided to focus on only the \textit{Maven}\footnote{Apache Maven is a build automation system mainly used for Java: \url{https://maven.apache.org/}} build automation system.
